---
title: "freeCurrencyApiR"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(freeCurrencyApiR)
```

freeCurrencyApiR provides functions for getting current and historical currency exchange rates.
Please refer to The Free Currency Converter API <https://free.currencyconverterapi.com> for
all endpoints available and rate limits. 

From the website:

```
Rate Limits of the Free API
Conversion Pairs per Request: 2
Number of Requests per Hour: 100
Date Range in History: 8 Days
Allowed Back in History: 1 Year(s)

Currency values are updated every 60 minutes. 
If you need a realtime web service or a service that updates more frequently, 
you may checkout the premium service at CurrencyConverterAPI.com.
```

## Install

```r
devtools::install_github("raybuhr/freeCurrencyApiR")
```

## Setup

You will need to [signup to get an API key](https://free.currencyconverterapi.com/free-api-key). Once you get the email with your key and confirm your email address by clicking through the included link, add this key to your `.Renviron`. If you are unfamiliar with this, you can run 

```r
usethis::edit_r_environ()
```

This will open up the `.Renviron` file for you to edit. Add a new line like this

```sh
FREE_CURRENCY_API_KEY=c224f8b5ee2f30e42256
```

## Examples

Get lists of the countries and currencies available:

```{r}
currencies <- free_currency_api_list_currencies()
currencies$results[[1]]
```

```{r}
countries <- free_currency_api_list_countries()
countries$results[[42]]
```

Get the current exchange rate between two currencies (based on a 60 minute refresh cache):

```{r}
free_currency_api_get_current(currency_from = "USD", currency_to = "CNY", compact = "ultra")
```

Get a `data.frame` of daily historical exchange rates between two currencies (No idea when the daily rate snapshot is taken):

```{r}
free_currency_api_get_historical(
  currency_from = "USD", currency_to = "INR", 
  start_date = "2018-04-01", end_date = "2018-04-08"
)
```

## Bugs/Issues

Report at [https://github.com/raybuhr/freeCurrencyApiR/issues](https://github.com/raybuhr/freeCurrencyApiR/issues)

## Contributing

Feel free to provide pull requests!
